Results

### 2018-03-30 02_analysis.Rmd
Use actual plots instead of faked unicode sparkbars

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(skimr)
library(janitor)
library(huxtable)
library(here)

@@

  data_frame(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE)) %>% 
    arrange(x) %>% 
    pull(fancy) %>% 
    paste(collapse = " | ")
}

numeric_summary <- function(x) {
  paste0("Mean: ", round(mean(x, na.rm = TRUE), 2), 
         " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2),
         " | ", inline_hist(x))
}

@@

  if (is.numeric(x)) {
    numeric_summary(x)
  } else {
    level_summary(x, variable, df)
  }
}

@@

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         Details = map2_chr(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  select(Variable = clean_name, everything())

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

  factor_summary <- data_frame(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE))

  inline_summary <- factor_summary %>% arrange(x) %>% 
    pull(fancy) %>% paste(collapse = " | ")

  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
    geom_bar(stat = "identity", fill = "black") +
    theme_spark()

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")

  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
                                       paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_bar, filename = file.path(here(), "output", "figures", "summary-table",
                                       paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

  output <- data_frame(spark = md_img, summary = inline_summary)
}

numeric_summary <- function(x, variable) {
  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))

  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
    geom_histogram(fill = "black", binwidth = 10) +
    theme_spark()

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")

  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
                                        paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_hist, filename = file.path(here(), "output", "figures", "summary-table",
                                        paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

  output <- data_frame(spark = md_img, summary = inline_summary)
}

@@

  if (is.numeric(x)) {
    numeric_summary(x, variable)
  } else {
    level_summary(x, variable, df)
  }
}

@@

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         summary = map2(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  unnest(summary) %>% 
  select(Variable = clean_name, N, ` ` = spark, Details = summary)
